---
title: "Cronin_#11"
author: "Hannah Cronin"
date: "2022-11-21"
output: html_document
---
```{r}
library(lpSolveAPI)
AP = make.lp(0,7)
```
Define variables:

X1 = shift 1
X2 = shift 2
X3 = shift 3
X4 = shift 4
X5 = shift 5
X6 = shift 6
X7 = shift 7

minimize: C(cost) = 775 X1 + 800 X2 + 800 X3 + 800 X4 + 800 X5 + 775 X6 + 750 X7
Constraints:
X2 + X3 + X4 + X5 + X6 >= 18 #Sunday workers
X3 + X4 + X5 + X6 + X7 >= 27 #Monday workers
X1 + X4 + X5 + X6 + X7 >= 22 #Tuesday workers
X1 + X2 + X5 + X6 + X7 >= 26 #Wednesday workers
X1 + X2 + X3 + X6 + X7 >= 25 #Thursday workers
X1 + X2 + X3 + X4 + X7 >= 21 #Friday workers
X1 + X2 + X3 + X4 + X5 >= 19 #Saturday workers

```{r}
set.objfn(AP, c(775, 800, 800, 800, 800, 775, 750))
lp.control(AP, sense = 'min')
set.type(AP, 1:7, type=c("integer"))
add.constraint(AP, c(0,1,1,1,1,1,0), ">=", 18) #Sunday workers
add.constraint(AP, c(0,0,1,1,1,1,1), ">=", 27) #Monday workers
add.constraint(AP, c(1,0,0,1,1,1,0), ">=", 22) #Tuesday workers
add.constraint(AP, c(1,1,0,0,1,1,1), ">=", 26) #Wednesday workers
add.constraint(AP, c(1,1,1,0,0,1,1), ">=", 25) #Thursday workers
add.constraint(AP, c(1,1,1,1,0,0,1), ">=", 21) #Friday workers
add.constraint(AP, c(1,1,1,1,1,0,0), ">=", 19) #Saturday workers

```

```{r}
Colnames = c('Shift1','Shift2','Shift3','Shift4','Shift5','Shift6','Shift7')
Rownames = c('Sunday workers','Monday workers','Tuesday workers','Wednesday workers','Thursday workers','Friday workers','Saturday workers')
dimnames(AP) = list(Rownames,Colnames)
```

```{r}
AP
```

```{r}
solve(AP)
get.objective(AP)
get.variables(AP)
get.constraints(AP)
```
## Min(Cost) = $26,425
## Min = 7 X1 + 0 X2 + 3 X3 + 2 X4 + 7 X5 + 6 X6 + 9 X7

## 7 Shift1 Workers, 0 Shift2 Workers, 3 Shift3 Workers, 2 Shift4 Workers, 7 Shift5 Workers, 6 Shift6 Workers, 9 Shift 7 Workers

## There would be 18 workers on Sunday, 27 workers on Monday, 22 Workers on Tuesday, 26 Workers on 
## Wednesday,25 Workers on Thursday, 21 Workers on Friday, and 19 Workers on Saturday

##This solution is all integer-based (no decimals as you cannot hire partial people).


