---
title: "assignment8"
author: "Hannah Cronin"
date: "2022-10-30"
output: html_document
---

```{r}
library(Benchmarking)
library(lpSolveAPI)
library(quadprog)
library(ucminf)
```

#setting up matrix
```{r}
inputs = matrix(c(150, 400, 320, 520, 350, 320, 0.2, 0.7, 1.2, 2.0, 1.2, 0.7), ncol = 2) #inputs
outputs = matrix(c(14000, 14000, 42000, 28000, 19000, 14000, 3500, 21000, 10500, 42000, 25000, 15000), ncol = 2)
colnames(inputs) <- c("staff hours/day","supplies/day")
colnames(outputs) <- c("reimbursed", "privately paid")
```

#VRS
```{r}
hv_vrs =  dea(inputs, outputs, RTS = "vrs") #solve lp problem
e_vrs = eff(hv_vrs)
e_vrs
peers(hv_vrs)
lambda(hv_vrs)
```
#FDH
```{r}
hv_fdh =  dea(inputs, outputs, RTS = "fdh") #solve lp problem
e_fdh = eff(hv_fdh)
e_fdh
peers(hv_fdh)
lambda(hv_fdh)
```
#CRS
```{r}
hv_crs =  dea(inputs, outputs, RTS = "crs") #solve lp problem
e_crs = eff(hv_crs)
e_crs
peers(hv_crs)
lambda(hv_crs)
```
#IRS
```{r}
hv_irs =  dea(inputs, outputs, RTS = "irs") #solve lp problem
e_irs = eff(hv_irs)
e_irs
peers(hv_irs)
lambda(hv_irs)
```
#DRS
```{r}
hv_drs =  dea(inputs, outputs, RTS = "drs") #solve lp problem
e_drs = eff(hv_drs)
e_drs
peers(hv_drs)
lambda(hv_drs)
```
#FRH
```{r}
hv_frh =  dea(inputs, outputs, RTS = "add") #solve lp problem
e_frh = eff(hv_frh)
e_frh
peers(hv_frh)
lambda(hv_frh)
```

```{r}
table = cbind(inputs, outputs, e_vrs, e_fdh, e_crs, e_irs, e_drs, e_frh)
table
```
# Under VRS, all facilities but 6 are efficient, which operates at 89.63% efficiency. DMU(6) is peers with 1,2,5 with weights of.40, .34, and .26.
# 
# Under FDH, all DMUs are efficient. There are no peers.
# Under CRS, DMU(1-4) are efficent, and DMUs(5,6) is 97.8% and 86.74% efficient respectively. DMU(5,6) have peer units with DMU(1,2,4) with weights of .2, .08, and .54 (DMU(5)) and .34, .39, and .13 (DMU(6)).
# Under IRS, all DMUs except DMU(6) are efficient, with DMU(6) having an efficiency of 89.63%. DMU(6) has peer units with DMU(1,2,5) with weights of .4, .34, .26.
# Under DRS, DMU(1-4) are efficent, and DMUs(5,6) is 97.8% and 86.74% efficient respectively. DMU(5,6) have peer units with DMU(1,2,4) with weights of .2, .08, and .54 (DMU(5)) and .34, .39, and .13 (DMU(6)).
# Under FRH,  all DMUs are efficient. There are no peers.

#FRH or FDH are the most suitable models for Hope Valley.