---
title: "assignment_9"
author: "Hannah Cronin"
date: "2022-11-06"
output: html_document
---

1/2.
Maximize: Z = P(Total Profit) - 6(Change in employement level) - 3(Decrease in next year's earning)
Maximize: Z = P - 6y1+ - 6y1- -3y2-

x1 = Product1
x2 = Product2
x3 = Product3
y1+ = increase in employment
y1- = decrease in employment
y2- = decrease in next year's earnings


(y1+ - y1-) = 6x1 + 4x2 + 5x3 - 50
(y2+ - y2-) = 8x1 + 7x2 + 5x3 - 75
y2+ = 0 #no harm in exceeding 75
P = 20x1 + 15x2 + 25x3

Maximize: Z = P - 6y1+ - 6y1- -3y2-

6x1 + 4x2 + 5x3 - (y1+ - y1-) = 50
8x1 + 7x2 + 5x3 - (y2+ - y2-) = 75
P = 20x1 + 15x2 + 25x3
xj >= 0, yi+ >=0, yi- >= 0, y2- < Z


#3 #I tried to use an LP file, however I could not get my computer to read. I will append to assignment anyways.
```{r}
# 6 decision variables, 0 constraints
library(lpSolveAPI)
decision = make.lp(0,6)
```

```{r}
set.objfn(decision, c(20,15,25,-6,-6,-3))
lp.control(decision, sense = 'max')
add.constraint(decision, c(6,4,5,1,-1,0), "=", 50) #constraint y1
add.constraint(decision, c(8,7,5,0,0,1), ">=", 75) #constraint y2
```

```{r}
Rownames = c('PX1','PX2','PX3','Y1M','Y1P','Y2M')
Colnames = c('y1','y2')
```

```{r}
decision
```

```{r}
solve(decision)
get.objective(decision)
get.variables(decision)
get.constraints(decision)
```
Maximum = 225 = 0x1 + 0x2 + 15x3 - 0y1m - 25y1p + 0 y2m
225 = 15(25) - 25(6)

Profit = 225 million dollars
Product 3 = 15 units
Labor = Change (grow)
Earnings = no decrease